Title: Vaucluse Usr Profile
========================================================

```{r set-options, echo=FALSE, cache=TRUE}
 options(width = 100)
# opts_chunk$set( echo=FALSE,cache=TRUE, fig.width=12, fig.height=6)
```

A overall view of the 5000 most frequent users in the department Vaucluse.

* total transactions number

* type of OD
    * OD frequented and repeated during the year
    * OD rarely taken
* type of user
    * OD type
        * mostly take repeated OD: with fixed routine and working shedule
        * take various OD during the daytime as well as night
    * by month
        * recently subscribe to our service
        rarely used our service 

```{r, echo=FALSE,cache=TRUE, fig.width=12, fig.height=6,width = 100}
temp<-count(List,c("OD_100","OD_50"))
temp<-temp[order(temp$freq,decreasing=TRUE),]
temp$per<-temp$freq/5000
temp[temp$per>.05,]

summary(List[,15:19])
```


* 1 case
    * OD_100==2 
    * P_Trx_100>.8
```{r,  echo=FALSE,cache=TRUE,fig.width=12,fig.height=12}
#temp<-List[List$OD_100==2 & List$P_Trx_100>.8,c(2,8:25)]
i<-List[List$OD_100==2 & List$P_Trx_100>.8,1][1:25]
temp<-ID_OD_2014[ID_OD_2014$Label %in% i,]
ggplot(temp,aes(Hour)) + geom_bar(binwidth=1) + xlim(0,25) + facet_wrap(~Label,ncol=5)

ggplot(temp,aes(Hour,fill=as.factor(Predicted))) + geom_bar(binwidth=1) + xlim(0,25) + facet_wrap(~Label,ncol=5)

ggplot(temp,aes(DOW,Hour)) + geom_point(alpha=.1) + facet_wrap(~Label,ncol=5)

```