---
title: "TimeSpace"
author: "Yuexiang Wang"
date: "16 July, 2015"
output: html_document
---

# Time Space
## ID1
```{r, echo=FALSE, cache=TRUE, fig.width=10, fig.height=6, warning=FALSE}
ggplot(ID1) +
  geom_point(aes(Date, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Date, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Date~Lng") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID1) +
  geom_point(aes(Date, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Date, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Date~Lat") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID1) +
  geom_point(aes(Date, Time)) +
  ggtitle("Date~Time") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID1) +
  geom_point(aes(Time, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Time, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Time~Lng") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID1) +
  geom_point(aes(Time, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Time, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Time~Lat") + theme(plot.title = element_text(size = rel(1)))

```

## ID2
```{r, echo=FALSE, cache=TRUE, fig.width=10, fig.height=6, warning=FALSE}
ggplot(ID2) +
  geom_point(aes(Date, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Date, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Date~Lng") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID2) +
  geom_point(aes(Date, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Date, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Date~Lat") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID2) +
  geom_point(aes(Date, Time)) +
  ggtitle("Date~Time") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID2) +
  geom_point(aes(Time, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Time, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Time~Lng") + theme(plot.title = element_text(size = rel(1)))

ggplot(ID2) +
  geom_point(aes(Time, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Time, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Time~Lat") + theme(plot.title = element_text(size = rel(1)))

```


## ID2 par DOW
```{r, echo=FALSE, cache=TRUE, fig.width=10, fig.height=6, warning=FALSE}
ggplot(ID2) +
  geom_point(aes(Date, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Date, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Date~Lng") + theme(plot.title = element_text(size = rel(1))) +
  facet_wrap(~DOW, ncol = 4)

ggplot(ID2) +
  geom_point(aes(Date, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Date, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Date~Lat") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~DOW, ncol = 4)

ggplot(ID2) +
  geom_point(aes(Date, Time)) +
  ggtitle("Date~Time") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~DOW, ncol = 4)

ggplot(ID2) +
  geom_point(aes(Time, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Time, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Time~Lng") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~DOW, ncol = 4)

ggplot(ID2) +
  geom_point(aes(Time, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Time, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Time~Lat") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~DOW, ncol = 4)
```


## ID12
```{r, echo=FALSE, cache=TRUE, fig.width=18, fig.height=6, warning=FALSE}
ggplot(ID12) +
  geom_point(aes(Date, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Date, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Date~Lng") + theme(plot.title = element_text(size = rel(1))) +
  facet_wrap(~Label, ncol = 2)

ggplot(ID12) +
  geom_point(aes(Date, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Date, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Date, xend = Date, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Date~Lat") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~Label, ncol = 2)

ggplot(ID12) +
  geom_point(aes(Date, Time)) +
  ggtitle("Date~Time") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~Label, ncol = 2)

ggplot(ID12) +
  geom_point(aes(Time, Elng, col = "Elng", shape = "Elng", alpha = .3)) +
  geom_point(aes(Time, Slng, col = "Slng", shape = "Slng", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elng, yend = Slng, alpha = .2)) +
  ggtitle("Time~Lng") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~Label, ncol = 2)

ggplot(ID12) +
  geom_point(aes(Time, Elat, col = "Elat", shape = "Elat", alpha = .3)) +
  geom_point(aes(Time, Slat, col = "Slat", shape = "Slat", alpha = .3)) +
  geom_segment(aes(x = Time, xend = Time, y = Elat, yend = Slat, alpha = .2)) +
  ggtitle("Time~Lat") + theme(plot.title = element_text(size = rel(1)))+
  facet_wrap(~Label, ncol = 2)
