---
title: "VIP_NP"
output: html_document
---

# NP

## Simple Stat Results
* Nb of Trx: `r nrow(NP)`
* First Date: `r min(NP$Date)`
* Last Date:  `r max(NP$Date)`
* Nb of each DOW in beween: 

```{r,echo=FALSE,fig.width=5,fig.height=3,cache=TRUE,warning=FALSE}
d1<-min(NP$Date)
d2<-max(NP$Date)
d <- JF[JF$Date >= d1 & JF$Date <= d2, ]
count(d,"DOW")
ggplot(d)+geom_bar(aes(DOW,fill=as.factor(JF)),binwidth=1)
#count(d[d$JF==1,],c("DOW","JF"))
```
```{r,echo=FALSE,fig.width=8,fig.height=3,cache=TRUE,warning=FALSE}
ggplot(NP)+geom_bar(aes(WOY),binwidth=1)+facet_wrap(~Year)
```

```{r,echo=FALSE,fig.width=5,fig.height=3,cache=TRUE,warning=FALSE}
center_M<-aggregate(NP[,18:19],list(NP$Month),mean)
names(center_M)[1]<-"Month"
ggplot(NP)+
  geom_point(aes(Slng,Slat,size=noPsg))+
  geom_point(data=center_M,aes(Slng,Slat,color=as.factor(Month)))

center_DOW<-aggregate(NP[,18:19],list(NP$DOW),mean)
names(center_DOW)[1]<-"DOW"
ggplot(NP)+
  geom_point(aes(Slng,Slat,size=noPsg))+
  geom_point(data=center_DOW,aes(Slng,Slat,color=as.factor(DOW)))
                    
PC<-ID_OD[ID_OD$Nom=="PC",]
center_DOW_PC<-aggregate(PC[,18:19],list(PC$DOW),mean)
names(center_DOW_PC)[1]<-"DOW"
ggplot(PC)+
  geom_point(aes(Slng,Slat,size=noPsg))+
  geom_point(data=center_DOW_PC,aes(Slng,Slat,color=as.factor(DOW)))

MD<-ID_OD[ID_OD$Nom=="MD"$ID_OD$Year==2014,]
center_DOW_MD<-aggregate(MD[,18:19],list(MD$DOW),mean)
names(center_DOW_MD)[1]<-"DOW"
ggplot(MD)+
  geom_point(aes(Slng,Slat,size=noPsg))+
  geom_point(data=center_DOW_MD,aes(Slng,Slat,color=as.factor(DOW)))

center_Month_MD<-aggregate(MD[,18:19],list(MD$Month),mean)
names(center_Month_MD)[1]<-"Month"
ggplot(MD)+
  geom_point(aes(Slng,Slat,size=noPsg))+
  geom_point(data=center_Month_MD,aes(Slng,Slat,color=as.factor(Month)))

ggplot(MD)+
  geom_bar(aes(Month),binwidth=1)+
  facet_wrap(~Year)

ggplot(MD)+
  geom_point(aes(Slng,Slat))+
  facet_grid(Year~Month)

# ggplot(NP,aes(Slng,Slat))+geom_boxplot()
# ggplot(NP,aes(y=Slng,x=Slat))+geom_boxplot()+coord_flip()
```


## 0. General Profile NP
```{r,echo=FALSE,fig.width=10,fig.height=10, cache=TRUE,warning=FALSE}
#NP<-ID_OD[ID_OD$Nom=="NP",] 

# ggplot()+geom_segment(data=na.omit(NP),aes(x=Elng, y=Elat,xend=Slng, yend=Slat), col="darkgreen",alpha=.2,lwd=1)+
#   geom_point(data=ID_OD,aes(Slng,Slat),col="darkblue",alpha=.2)+
#    geom_point(data=gares_geo[gares_geo$Societe != 5,],aes(Lng,Lat),alpha=.2,size=3)+   guides(fill=FALSE)

Sor<-count(NP,"Sor")
Entr<-count(NP,"Entr")
OD<-count(NP,c("Entr","Sor"))
OD<-OD[order(OD$freq,decreasing=TRUE),] 

names(Sor)[1]<-"Cde"
names(Entr)[1]<-"Cde"
Sor<-merge(x=Sor,gares_geo,by="Cde")
Entr<-merge(Entr,gares_geo,by="Cde")
Sor<-Sor[order(Sor$freq,decreasing=TRUE),]
Entr<-Entr[order(Entr$freq,decreasing=TRUE),]


ggplot(NP)+
  geom_segment(aes(x=Elng, y=Elat,xend=Slng, yend=Slat), alpha=.4,lwd=1,
               col="#FFCC33")+
  geom_point(data=Sor,aes(Lng, Lat,size=freq), col="Red")+
  geom_point(data=gares_geo,aes(Lng,Lat),size=3,alpha=.2,shape=3)+
  geom_point(data=gare_SO,aes(Lng, Lat, color="S.O."), size=3, shape=3)+
  ylim(c(42,46.5))+xlim(c(-1.5,7.5))+
  theme(legend.position=c(.95,.9),plot.title = element_text(size=20, face="bold")) +
  ggtitle("Sor & OD")
```

## Clustering Result
```{r,echo=FALSE,fig.width=10,fig.height=10, cache=TRUE,warning=FALSE}

ggplot(Kres)+
  geom_segment(aes(x=Elng, y=Elat,xend=Slng, yend=Slat,color=as.factor(Cluster)), alpha=.4,lwd=1,arrow=arrow(length = unit(0.1,"cm")))+
  geom_point(data=Sor,aes(Lng, Lat,size=freq), col="Red")+
  geom_point(data=gares_geo,aes(Lng,Lat),size=3,alpha=.2,shape=3)+
  geom_point(data=gare_SO,aes(Lng, Lat, color="S.O."), size=3, shape=3)+
  ylim(c(42,46.5))+xlim(c(-1.5,7.5))+
  theme(legend.position=c(.95,.9),plot.title = element_text(size=20, face="bold")) +
  ggtitle("Sor & OD")
```



## 1. General Profile NP
```{r,echo=FALSE,cache=TRUE,fig.width=6,fig.height=6}
library(ggplot2)
library(plyr)
library(gridExtra)
 
p1<-ggplot(NP,aes(Year))+geom_bar()
p2<-ggplot(NP,aes(Hour))+geom_density()
p3<-ggplot(NP,aes(DOW))+geom_density()
p4<-ggplot(NP,aes(perPsg))+geom_density()

grid.arrange(p1,p2,p3,p4, ncol=2)
```

## 2. NP's OD
```{r,echo=FALSE,cache=TRUE}
temp<-NP[NP$Year==2014,]
temp2<-count(temp,c("Entr","Sor"))
temp2<-temp2[order(temp2$freq,decreasing=TRUE),]
print(paste0("number of OD by NP in 2014: ",nrow(temp2)))
head(temp2)
```
 
### 2.1 NP's AR-DT is between Cavaillon(220) and Avignon(211): 
**DOW/H**
*  goes to work at 6 or 7h
*	returns at 17h
```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=5}
i=2
nrow(ID_OD[ID_OD$Nom==ID_ref$Nom[i],])
count(ID_OD[ID_OD$Nom==ID_ref$Nom[i] & ID_OD$noPsg>seuil & ID_OD$Hour %in% periodAller & ID_OD$DOW %in% jrOuvert,],c("Nom","Entr","Sor"))
count(ID_OD[ID_OD$Nom==ID_ref$Nom[i] & ID_OD$noPsg>seuil & ID_OD$Hour %in% periodRetour & ID_OD$DOW %in% jrOuvert,],c("Nom","Entr","Sor"))

temp_AR<-ID_OD[ID_OD$Nom==ID_ref$Nom[i] & 
                 ((ID_OD$Entr==25004220 & ID_OD$Sor==25004211)|
                 (ID_OD$Entr==25004211 & ID_OD$Sor==25004220)),] 
temp_title<-"NP: Aller-Retour"
ggplot(temp_AR,aes(Hour,fill=as.factor(DOW)))+geom_bar(binwidth=1) + xlim(c(0,25)) + ggtitle(temp_title)  

ggplot(temp_AR,aes(Hour,fill=as.factor(Predicted)))+geom_bar(binwidth=1) + xlim(c(0,25)) + ggtitle(temp_title)  
```

**Hour**
```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=5}
temp_Aller<-ID_OD[ID_OD$Nom==ID_ref$Nom[i] & 
                 (ID_OD$Entr==25004220 & ID_OD$Sor==25004211) ,] 
temp_Retour<-ID_OD[ID_OD$Nom==ID_ref$Nom[i] & 
                 (ID_OD$Entr==25004211 & ID_OD$Sor==25004220) ,]

ggplot(temp_AR,aes(Date,Time))+geom_point()
ggplot(temp_Aller,aes(factor(DOW),y=Time))+geom_boxplot()
ggplot(temp_Retour,aes(factor(DOW),y=Time))+geom_boxplot()
```


**DOW/H points**
```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=5}

temp2<-NP[NP$Entr==25004220 & NP$Sor==25004211,]
p1<-ggplot(temp2,aes(Hour,DOW,fill=(as.factor(Predicted))))+geom_tile(binwidth=1)+xlim(c(0,25))+ylim(c(0,7)) +ggtitle("Aller")+guides(fill=FALSE)

temp3<-NP[NP$Entr==25004211 & NP$Sor==25004220,]
p3<-ggplot(temp3,aes(Hour,DOW,fill=(as.factor(Predicted))))+geom_tile(binwidth=1)+xlim(c(0,25))+ylim(c(0,7)) +ggtitle("Retour")+guides(fill=FALSE)

grid.arrange(p1,p3,ncol=2)
```

**DOW/WOY**
*	blank line: week without AR-DT (vacations)
*	blank spot: JF or VS or take other route (activity afterwork)
```{r,echo=FALSE,cache=TRUE,fig.width=10,fig.height=5}

ggplot(temp2,aes(WOY,DOW,fill=as.factor(DOW)))+geom_tile(binwidth=1)+xlim(c(0,52))+ylim(c(0,7)) +ggtitle("Aller")
ggplot(temp3,aes(WOY,DOW,fill=as.factor(DOW)))+geom_tile(binwidth=1)+xlim(c(0,52))+ylim(c(0,7)) +ggtitle("Retour")

ggplot(temp2,aes(WOY,DOW,fill=(as.factor(Predicted))))+geom_tile(binwidth=1)+xlim(c(0,52))+ylim(c(0,7)) +ggtitle("Aller")
#+guides(fill=FALSE)
ggplot(temp3,aes(WOY,DOW,fill=(as.factor(Predicted))))+geom_tile(binwidth=1)+xlim(c(0,52))+ylim(c(0,7)) +ggtitle("Retour")
#+guides(fill=FALSE)
```

**Result**
*   Statistics
```{r,echo=TRUE,cache=TRUE}
count(temp2,c("DOW","Hour","Per"))
count(temp2,"Per")
count(temp2,"Predicted")

```
